Fictitious Play in Network Aggregative Games

### 2021-03-26 Documents/FP in NAGs/FPNAG.tex
Added Responses to IJCAI

	I've spent some time trying to show convergence of the CTFP to a Nash Equilibrium, without the
	requirement that $w_{ii} = 0$. Unfortunately, it doesn't look like that is the case in general,
	at least with the other assumptions that we have made. Perhaps changing the requirement of the
	payoff functions or the aggregation method (e.g. to a non-linear one) would influence this, but
	for the bimatrix games that we've looked at so far, no luck.
	We can, however, say that there is a fixed point since the solution $\alpha(t; m)$, for any CTFP
	$m$ maps from a compact space to itself. Therefore, any sequence $\{\alpha(\tau_q; m)\}$ where
	$\tau_q \rightarrow \infty$ as $q \rightarrow \infty$ has all of its elements inside a compact
	set. Therefore, by the Bolzano-Wierstrass Theorem, this sequence has at least one limit point.
	We can say that this limit point corresponds to an NE when $w_{ii} = 0$, but I am trying to
	determine any other structure of the limit point for when this does not hold. For example, is it
	part of the `no regret' set?

>>>>

	I've spent some time trying to show convergence of the CTFP to a Nash Equilibrium, without the
	requirement that $w_{ii} = 0$. Unfortunately, it doesn't look like that is the case in general,
	at least with the other assumptions that we have made. Perhaps changing the requirement of the
	payoff functions or the aggregation method (e.g. to a non-linear one) would influence this, but
	for the bimatrix games that we've looked at so far, no luck.
	We can, however, say that there is at least one accumulation point since the solution $\alpha(t;
	m)$, for any CTFP
	$m$ maps from a compact space to itself. Therefore, any sequence $\{\alpha(\tau_q; m)\}$ where
	$\tau_q \rightarrow \infty$ as $q \rightarrow \infty$ has all of its elements inside a compact
	set. Therefore, by the Bolzano-Wierstrass Theorem, this sequence has at least one limit point.
	We can say that such a limit point corresponds to an NE when $w_{ii} = 0$, but I am trying to
	determine any other structure of the limit point for when this does not hold. For example, is
	the limit set a singleton (i.e. a fixed point) or a set. What are the properties of this set?
	Do they satisfy the no-regret criterion?	\newpage
